Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2013-11-05 writeups/proposal/proposal.tex
foo
Former-commit-id: c8b9b1ca53b26262082d90559715ad843dc7ca63 [formerly 0782f334feafc62beedfd0e7527d5e1d079bbe51]
Former-commit-id: 58595f5bc64a148f7486546d4f587a0ed36b9ea8

The Latex and SuperUser sites are not nearly as popular as StackOverflow currently.
The sites have roughly \num{50000} and \num{189000} questions respectively compared to \num{5000000} questions on StackOverflow.
It may be the case that StackExchange decided to try out a tag recommendation system on a few of their smaller sites first, before deploying this type of system on their most popular StackOverflow site.
Or it is possible that their current tag recommendation system is not efficient enough to work with the demand of the StackOverflow site.
Nonetheless, it is encouraging that StackExchange finds tag recommendation models beneficial to the user and has started to add them to their question and answer sites.

@@

>>>>

The exact tag-recommendation algorithm used for the LaTeX and SuperUser sites is not publicized.
StackExchange appears to be using something more sophisticated than simply looking for words in the title and body of the post that are tags, as the algorithm has not yet been deployed for the busiest StackOverflow site.
The Latex and SuperUser sites are not nearly as popular as StackOverflow currently.
The sites have roughly \num{50000} and \num{189000} questions respectively compared to \num{5000000} questions on StackOverflow.

So it stands to reason that the algorithm is relatively complex, and there are possible scaling and efficiency concerns with the algorithm's implementation.
Or it is also possible that StackExchange decided to try out a tag recommendation system on a few of their smaller sites first, before deploying this type of system on their most popular StackOverflow site.
Nonetheless, it is encouraging that StackExchange finds tag recommendation models beneficial to the user and has started to add them to their question and answer sites.

@@

Google+'s tag-recommendation algorithm is not publicized, but it appears to be rather sophisticated.
Looking at the example post in Figure \ref{figGoogle+Hashtags}, \#BusterPosey is suggested without having that specific word in the post.
Also \textcite{GoogleKeynote2013} mentioned that Google uses its sophisticated image recognition software to suggest hashtags for images that are included in the post (e.g., \#EiffelTower),
even when the post does not have any keywords to provide additional context.
